\textbf{SPECFEM3D}\\ \textbf{Cartesian}\\ \textbf{User Manual}

### 2023-05-04 doc/USER_MANUAL/02_getting_started.tex

\noindent
SPECFEM3D now supports CUDA and HIP GPU acceleration.
When compiling for GPU cards, you can enable the CUDA version with:
\begin{verbatim}
  ./configure --with-cuda ..
\end{verbatim}
or
\begin{verbatim}
  ./configure --with-cuda=cuda9 ..
\end{verbatim}
where for example \texttt{cuda4,cuda5,cuda6,cuda7,..} specifies the target GPU architecture of your card,
(e.g., with CUDA 9 this refers to Volta V100 cards), rather than the installed version of the CUDA toolkit.
Before CUDA version 5, one version supported basically one new architecture and needed a different kind of compilation.
Since version 5, the compilation has stayed the same, but newer versions supported newer architectures.
However at the moment, we still have one version linked to one specific architecture:
\begin{verbatim}
- CUDA 4 for Tesla,   cards like K10, Geforce GTX 650, ..
- CUDA 5 for Kepler,  like K20
- CUDA 6 for Kepler,  like K80
- CUDA 7 for Maxwell, like Quadro K2200
- CUDA 8 for Pascal,  like P100
- CUDA 9 for Volta,   like V100
- CUDA 10 for Turing, like GeForce RTX 2080
- CUDA 11 for Ampere, like A100
\end{verbatim}
So even if you have the new CUDA toolkit version 11, but you want to run on say a K20 GPU, then you would still configure with:
\begin{verbatim}
  ./configure --with-cuda=cuda5
\end{verbatim}
The compilation with the cuda5 setting chooses then the right architecture (\texttt{-gencode=arch=compute\_35,code=sm\_35} for K20 cards).\newline

>>>>

\noindent
SPECFEM3D now supports CUDA and HIP GPU acceleration.
When compiling for GPU cards, you can enable the CUDA version with:
\begin{verbatim}
  ./configure --with-cuda ..
\end{verbatim}
or
\begin{verbatim}
  ./configure --with-cuda=cuda9 ..
\end{verbatim}
where for example \texttt{cuda4,cuda5,cuda6,cuda7,..} specifies the target GPU architecture of your card,
(e.g., with CUDA 9 this refers to Volta V100 cards), rather than the installed version of the CUDA toolkit.
Before CUDA version 5, one version supported basically one new architecture and needed a different kind of compilation.
Since version 5, the compilation has stayed the same, but newer versions supported newer architectures.
However at the moment, we still have one version linked to one specific architecture:
\begin{verbatim}
- CUDA 4 for Tesla,   cards like K10, Geforce GTX 650, ..
- CUDA 5 for Kepler,  like K20
- CUDA 6 for Kepler,  like K80
- CUDA 7 for Maxwell, like Quadro K2200
- CUDA 8 for Pascal,  like P100
- CUDA 9 for Volta,   like V100
- CUDA 10 for Turing, like GeForce RTX 2080
- CUDA 11 for Ampere, like A100
- CUDA 12 for Hopper, like H100
\end{verbatim}
So even if you have the new CUDA toolkit version 11, but you want to run on say a K20 GPU, then you would still configure with:
\begin{verbatim}
  ./configure --with-cuda=cuda5
\end{verbatim}
The compilation with the cuda5 setting chooses then the right architecture (\texttt{-gencode=arch=compute\_35,code=sm\_35} for K20 cards).\newline
